|

### 2021-08-14 nuova-final-draft.Rmd
sigma algebra

\section{Notation}
Let us fix the basic notation that will be employed henceforth. Upper case letters, e.g. $X_t, Y_t,$ denote random variables, while lower case letters 
denote the realizations. Finite sequences are made compact using the semi-colon notation, e.g. $x_{0:t}=(x_0, x_1, \dots, x_t)$ for some $t \geq 0.$ The sets of outcomes are denoted by upper case calligraphic letters, e.g. $\mathcal{X}, \mathcal{Y}.$  The $\sigma$-algebra
of a set $\mathcal{X}$ reads $\mathcal{B}(\mathcal{X}).$ The pair $(\mathcal{X}, \mathcal{B}(\mathcal{X}))$ is a measurable space.
The densities are represented with lower case cursive letters. For example, the density of $X_t$ in $x_t$ is $p_t^\theta(x_t),$ where $\theta\in\Theta$ is some (eventually known) vector, while the density 
of $X_t$ in $x_t,$ given that $X_{t-1}$ has previously taken value $x_{t-1},$ is $p_t^\theta(x_t\mid x_{t-1}).$  Note that $p_t^\theta(x_t\mid x_{t-1})$ is a member of the parametric family with parameters $(\theta, x_{t-1})$.
The probability distribution of a random variable $X_t$ is represented by $\mathbb{P}_t(dx_t),$ while the probability distribution of a sequence $X_{0:t}$ is represented by $\mathbb{P}_t(dx_{0:t}).$ The Dirac measure, i.e., the measure that assigns probability $1$ to the singleton $\{x\},$ is denoted by $\delta_x(dy)$.The expectation operator is denoted by $\mathbb{E},$ where the section of $\mathbb{E}$ at $\mathbb{Q},$ i.e., $\mathbb{E}_{\mathbb{Q}}$ denotes the operator computed with respect to the probability distribution $\mathbb{Q}.$ 
Let $\varphi$ be a function defined on the random variable $X\propto\mathbb{Q}.$ Then, we denote the expected value of $\varphi(X)$ with 
$$
    \mathbb{E}_{\mathbb{Q}}[\varphi(X)]=
    \int_{\mathcal{X}}\varphi(x)\mathbb{Q}(dx).
$$
Convergence in distribution is denoted with the symbol $\implies.$ So, $X\implies\N(0,1)$ means that the random variable $X$ converges in distribution to a normal Gaussian.

>>>>

\section{Notation}
Let us fix the basic notation that will be employed henceforth. Upper case letters, e.g. $X_t, Y_t,$ denote random variables, while lower case letters 
denote the realizations. Finite sequences are made compact using the semi-colon notation, e.g. $x_{0:t}=(x_0, x_1, \dots, x_t)$ for some $t \geq 0.$ The sets of outcomes are denoted by upper case calligraphic letters, e.g. $\mathcal{X}, \mathcal{Y}.$  A generic $\sigma$-algebra
of a set $\mathcal{X}$ reads $\mathcal{B}(\mathcal{X}).$ The pair $(\mathcal{X}, \mathcal{B}(\mathcal{X}))$ is a measurable space.
The densities are represented with lower case cursive letters. For example, the density of $X_t$ in $x_t$ is $p_t^\theta(x_t),$ where $\theta\in\Theta$ is some (eventually known) vector, while the density 
of $X_t$ in $x_t,$ given that $X_{t-1}$ has previously taken value $x_{t-1},$ is $p_t^\theta(x_t\mid x_{t-1}).$  Note that $p_t^\theta(x_t\mid x_{t-1})$ is a member of the parametric family with parameters $(\theta, x_{t-1})$.
The probability distribution of a random variable $X_t$ is represented by $\mathbb{P}_t(dx_t),$ while the probability distribution of a sequence $X_{0:t}$ is represented by $\mathbb{P}_t(dx_{0:t}).$ The Dirac measure, i.e., the measure that assigns probability $1$ to the singleton $\{x\},$ is denoted by $\delta_x(dy)$.The expectation operator is denoted by $\mathbb{E},$ where the section of $\mathbb{E}$ at $\mathbb{Q},$ i.e., $\mathbb{E}_{\mathbb{Q}}$ denotes the operator computed with respect to the probability distribution $\mathbb{Q}.$ 
Let $\varphi$ be a function defined on the random variable $X\propto\mathbb{Q}.$ Then, we denote the expected value of $\varphi(X)$ with 
$$
    \mathbb{E}_{\mathbb{Q}}[\varphi(X)]=
    \int_{\mathcal{X}}\varphi(x)\mathbb{Q}(dx).
$$
Convergence in distribution is denoted with the symbol $\implies.$ So, $X\implies\N(0,1)$ means that the random variable $X$ converges in distribution to a normal Gaussian.
